stats-project

### 2020-12-06 R - Deliverable/MSDS-6371---Project.Rmd
final changes

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(car)
library(data.table)
library(mltools)
library(olsrr)
library(scales)
library(caret)

# options
#options(scipen = 999)
```

```{r message=FALSE, warning=FALSE}
data_train= read_csv("../Data/train.csv")
data_test = read_csv("../Data/test.csv")
#Convert <chr> to <fctr>
data_train = as.data.frame(unclass(data_train))
data_train$Neighborhood = as.factor(data_train$Neighborhood)
data_train$HouseStyle = as.factor(data_train$HouseStyle)
data_train$KitchenQual = as.factor(data_train$KitchenQual)
data_train$SaleCondition = as.factor(data_train$SaleCondition)

data_test = as.data.frame(unclass(data_test))
data_test$Neighborhood = as.factor(data_test$Neighborhood )
data_test$HouseStyle = as.factor(data_test$HouseStyle)
data_test$KitchenQual = as.factor(data_test$KitchenQual)
data_test$SaleCondition = as.factor(data_test$SaleCondition)
# add new remodel variable
data_train$Remodel =ifelse(data_train$YearBuilt==data_train$YearRemodAdd, 0, 1)
data_test$Remodel =ifelse(data_test$YearBuilt==data_test$YearRemodAdd, 0, 1)
data_train$GrLivArea2 = data_train$GrLivArea^2
data_test$GrLivArea2 = data_test$GrLivArea^2
summary(data_train)
summary(data_test)
head(data_train)

@@

# 2.5Fin does not exist in test data so changing it to 1.5Unf
train_data_q2$HouseStyle = as.character(train_data_q2$HouseStyle)
train_data_q2 = train_data_q2 %>%   mutate_at(vars(HouseStyle) ,     ~ifelse(.x=="2.5Fin","1.5Unf",.x  ))

train_data_q2$HouseStyle = as.factor(train_data_q2$HouseStyle)

train_data_q2_process = preProcess(train_data_q2[,2:20], method=c("center", "scale"))
train_data_q2 =  predict(train_data_q2_process, train_data_q2)

@@

# Inpute = NA in test data
test_data_q2= test_data_q2 %>% mutate_at(vars(GarageCars),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
test_data_q2= test_data_q2 %>% mutate_at(vars(BsmtFullBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
test_data_q2= test_data_q2 %>% mutate_at(vars(BsmtHalfBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))

summary(test_data_q2)
#nrow(test_data_q2)
unique(train_data_q2$HouseStyle)
unique(test_data_q2$HouseStyle)

@@

```{r}
train_data_q2
test_data_q2
```

#look for missing values
missing.values <- train_data_q2 %>%
    gather(key = "key", value = "val") %>%
    mutate(is.missing = is.na(val)) %>%
    group_by(key, is.missing) %>%
    summarise(num.missing = n()) %>%
    filter(is.missing==T) %>%
    select(-is.missing) %>%
    arrange(desc(num.missing))

missing.values
```

#lm_fit_experiment = lm(SalePrice ~. -Id-Utilities-Street-PoolQC-MiscFeature-Alley-Fence-FireplaceQu-LotFrontage-GarageCond-GarageFinish-GarageQual-GarageType-GarageYrBlt-BsmtExposure-BsmtFinType2-BsmtCond-BsmtFinType1-BsmtQual-MasVnrArea-MasVnrType-Electrical  , data = train)
#lm_fit_experiment
#Neighborhood_Blmngtn

#summary(lm_fit_experiment)
#confint(lm_fit_experiment,  level=0.995)

@@

```{r}
names(one_encode_train_data_q2)
```

#	ANALYSIS 2
```{r message=FALSE, warning=FALSE}

one_encode_train_data_q2 =  one_hot(as.data.table(train_data_q2, dropUnusedLevels=TRUE))
one_encode_train_data_q2
one_encode_test_data_q2 =  one_hot(as.data.table(test_data_q2, dropUnusedLevels=TRUE))

@@

summary(lm_fit_q2)
confint(lm_fit_q2,  level=0.995)
```
## Model Selection
### Stepwise
```{r message=FALSE, warning=FALSE}
#Stepwise Selection
stepwise_fit = ols_step_both_p(lm_fit_q2, pent =0.05, prem=0.05)
stepwise_fit
```
```{r}
stepwise_fit$predictors
```

@@

write_csv(stepwise_submission, "../kaggleData/stepwiseSelectionPredictions.csv")

nrow(stepwise_submission)
sum(is.na(stepwise_submission))
stepwise_submission_na <- stepwise_submission %>% filter_all(any_vars(is.na(.))) 
stepwise_submission_na
```

@@

```{r}
fw_model = fw_fit$model
ols_press(fw_model)
summary(fw_model)
confint(fw_model)

@@

fw_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=fw_predictions)
fw_submission
write_csv(fw_submission, "../kaggleData/forward SelectionPredictions.csv")

nrow(fw_submission)
sum(is.na(fw_submission))
fw_submission_na <- fw_submission %>% filter_all(any_vars(is.na(.))) 
fw_submission_na
```

@@

```{r}
bw_model = bw_fit$model
ols_press(bw_model)
formatC(ols_press(bw_model), format = "e", digits = 6)
summary(bw_model)
confint(bw_model)
```

@@

bw_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=bw_predictions)
bw_submission
write_csv(bw_submission, "../kaggleData/backwardsSelectionPredictions.csv")

@@

```
```{r}
custom_train_data_exclude

@@

```{r}
# outliers list
 outliers_forward = c(4, 54,   59,   66,   67,   70,   94,  119,  121,  138,  152,  154,  164,  179,  186,  209,  219,  239,  250,  252,  262,  305,  314,  321,  322,  331,  336,  337,  349,  350,  363,  384,  385,  401,  427,  439,  441,  474,  478,  497,  524,  528,  530,  560,  567,  569,  582,  584,
586,  589,  592,  598,  608,  622,  633,  636,  641,  643,  656,  662,  665,  682,  686,  689,  692,  703,  713,  725,  745,  770,  775,  779,  799,  804,  811,  813,  823,  826,  841,  876,  878,  886,  898,  899,  926,  940,  962,  971, 1018, 1025, 1032, 1045, 1047, 1049, 1063, 1066,
1069, 1128, 1143, 1156, 1169, 1170, 1174, 1176, 1182, 1183, 1217, 1268, 1269, 1285, 1299, 1311, 1323, 1325, 1327, 1329, 1360, 1387, 1389, 1397, 1416, 1424, 1441)

@@

#custom_train_data = data_train

@@

custom_train_data_process = preProcess(custom_train_data[,2:20], method=c("center", "scale"))
custom_train_data =  predict(custom_train_data_process, custom_train_data)

custom_test_data = data_test %>%  select(Id, selected_features_q2)
custom_test_data =  predict(custom_train_data_process, test_data_q2)

@@

one_encode_custom_train_data
```

@@

```{r}
custom_model = custom_fit$model
ols_press(custom_model)
formatC(ols_press(custom_model), format = "e", digits = 6)
summary(custom_model)
confint(custom_model)
```

@@

ols_plot_resid_fit(custom_model)
ols_plot_resid_pot(custom_model)
ols_pred_rsq(custom_model)
plot(custom_fit)
```
```{r}
enco
custom_model_outliers$outliers$observation

@@

custom_submission = data.frame(Id= one_encode_custom_test_data$Id, SalePrice=custom_predictions)
custom_submission
write_csv(custom_submission, "../kaggleData/customSelection1Predictions.csv")
```

@@

one_encode_custom_train_data_model2 = one_encode_custom_train_data
one_encode_custom_train_data_model2 =  one_encode_custom_train_data %>% mutate( index=row_number())

custom_model_1_outliers = c(4,    6,   13,   28,   30,   55,   96,  106,  107,  135,  143,  157,  163,  183,  208,  215,  296,  302,  304,  347,  354,  357,  375,  384,  385,  387,  415,  421,  426,  434,  437,  443,  444,  464,  498,  504,  520,  525,  556,  587,  600,  603,  616,  618,  628,  636,  641,  652,
 661,  671,  679,  697,  736,  751,  770,  786,  813,  842,  877,  886,  887,  900,  903,  932,  941,  946,  950,  952,  976, 1001, 1004, 1030, 1033, 1047, 1058, 1064, 1065, 1069, 1079, 1117, 1120, 1124, 1133, 1137, 1138, 1144, 1147, 1173, 1204, 1229, 1234, 1240, 1245, 1265, 1267, 1270,
1277, 1284, 1311)

one_encode_custom_train_data_model2 = one_encode_custom_train_data_model2[!(one_encode_custom_train_data_model2$index %in% custom_model_1_outliers), ]
one_encode_custom_train_data_model2

#get original data again without all the outliers. This way we can scale it using only the values we will utilize, we do this to avoid data leaking
final_one_encode_custom_train_data_model2 = data_train[(data_train$Id %in% one_encode_custom_train_data_model2$Id), ]
final_one_encode_custom_train_data_model2
```
```{r}
# do all the data preprossesing again

final_one_encode_custom_train_data_model2 = final_one_encode_custom_train_data_model2 %>% select(Id, selected_features_q2,  SalePrice)

# 2.5Fin does not exist in test data so changing it to 1.5Unf
final_one_encode_custom_train_data_model2$HouseStyle = as.character(final_one_encode_custom_train_data_model2$HouseStyle)
final_one_encode_custom_train_data_model2 = final_one_encode_custom_train_data_model2 %>%   mutate_at(vars(HouseStyle) ,     ~ifelse(.x=="2.5Fin","1.5Unf",.x  ))

@@

custom2_train_data_process = preProcess(final_one_encode_custom_train_data_model2[,2:20], method=c("center", "scale"))
final_one_encode_custom_train_data_model2 =  predict(custom2_train_data_process, final_one_encode_custom_train_data_model2)

@@

# Inpute = NA in test data
final_custom_test_data= final_custom_test_data %>% mutate_at(vars(GarageCars),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
final_custom_test_data= final_custom_test_data %>% mutate_at(vars(BsmtFullBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
final_custom_test_data= final_custom_test_data %>% mutate_at(vars(BsmtHalfBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))

@@

#Refferences: Neighborhood_BrkSide KitchenQual_TA HouseStyle_SLvl SaleCondition_Partial
# Manual exclusion:
# take away PoolArea due to 0 variance warning
#SaleCondition_AdjLand:GrLivArea2           NA         NA      NA       NA    
#SaleCondition_Alloca:GrLivArea2            NA         NA      NA       NA 
#LotArea:SaleCondition_AdjLand              NA         NA      NA       NA    
#LotArea:SaleCondition_Alloca               NA         NA      NA       NA    
#SaleCondition_Alloca:BedroomAbvGr          NA         NA      NA       NA

@@

summary(lm_fit_custom2)
ols_press(lm_fit_custom2)

```
```{r message=FALSE, warning=FALSE}

@@

```{r}
custom_model2 = custom_fit2$model
ols_press(custom_model2)
formatC(ols_press(custom_model2), format = "e", digits = 6)
summary(custom_model2)
confint(custom_model2)
```

```{r}
ols_plot_cooksd_bar(custom_model2)

custom_model_outliers2 = ols_plot_cooksd_bar(custom_model2, print_plot=F)
custom_model_outliers2

ols_plot_dffits(custom_model2)
ols_plot_diagnostics(custom_model2)

ols_plot_resid_fit(custom_model2)
ols_plot_resid_pot(custom_model2)
ols_pred_rsq(custom_model2)
plot(custom_fit2)
```

@@

custom_model_outliers2$outliers$observation

@@

custom_predictions2 = c(predict(custom_model2, newdata = one_encode_custom_test_data2))

custom_predictions2 = data.frame(Id= one_encode_custom_test_data2$Id, SalePrice=custom_predictions2)
custom_predictions2
write_csv(custom_predictions2, "../kaggleData/customSelection2Predictions.csv")
```
```{r}
one_encode_custom_test_data2
```
```{r}
custom_model2

@@

>>>>

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(ggpubr)
library(ggplot2)
library(car)
library(data.table)
library(mltools)
library(olsrr)
library(scales)
library(caret)
library(dataPreparation)
library(regclass)
# options
#options(scipen = 999)
```

```{r message=FALSE, warning=FALSE}
data_train= read_csv("../Data/train.csv")
data_test = read_csv("../Data/test.csv")
#Convert <chr> to <fctr>
data_train = as.data.frame(unclass(data_train))
data_train$Neighborhood = as.factor(data_train$Neighborhood )
data_test = as.data.frame(unclass(data_test))
data_test$Neighborhood = as.factor(data_test$Neighborhood )
# add new remodel variable
data_train$Remodel =ifelse(data_train$YearBuilt==data_train$YearRemodAdd, 0, 1)
data_test$Remodel =ifelse(data_test$YearBuilt==data_test$YearRemodAdd, 0, 1)
data_train$GrLivArea2 = data_train$GrLivArea^2
data_test$GrLivArea2 = data_test$GrLivArea^2
dim(data_train)
dim(data_test)

```{r}
 # In this function we will handle missing values ffor numerical and factor columns 
impute_missing_values_func = function(data){

  # create list of  Numerical Columns names
    nums_col = data %>% purrr::discard(~!is.numeric(.)) %>% names

    # create list of  factor Columns names
    char_col = data %>% purrr::discard(~!is.character(.)) %>% names

    # Create a new dataframe for q2 train data, this is a copy of the original train DF
    treated_data = data

    # Input NA's in numerical columns with the mediam value per column
    for (i in nums_col){
     treated_data = treated_data %>% mutate_at(vars(UQ(as.name(i))),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
    }

    # Create a new factor level called None for each NA in factor columns
    for (i in char_col){
      treated_data[i][is.na(treated_data[i])] = "None"
    }

    return(treated_data)

}

show_missing_values = function(data){
      missing.values <- data %>%
        gather(key = "key", value = "val") %>%
        mutate(is.missing = is.na(val)) %>%
        group_by(key, is.missing) %>%
        summarise(num.missing = n()) %>%
        filter(is.missing==T) %>%
        select(-is.missing) %>%
        arrange(desc(num.missing))

    print(missing.values$key)

}

```{r message=FALSE, warning=FALSE}
# Let's handle the missing values
# show missing values on train DF

#show_missing_values(data_train)
#show_missing_values(data_test)
#data_train_q2 = impute_missing_values_func(data_train)
#data_test_q2 = impute_missing_values_func(data_test)

# show missing values on treated train DF - there should be 0
#show_missing_values(data_train_q2)
#show_missing_values(data_test_q2)

#encoding = build_encoding(data_set = data_train_q2, cols = "auto", verbose = TRUE)
#enconded_data_train_q2 = one_hot_encoder(data_set = data_train_q2, encoding = encoding, drop = TRUE, verbose = F)
#enconded_data_test_q2 = one_hot_encoder(data_set = data_test_q2, encoding = encoding, drop = TRUE, verbose = F)
#print(dim(enconded_data_train_q2))
#print(dim(enconded_data_test_q2))

@@

# 2.5Fin does not exist in test data so changing it to 1.5Unf
train_data_q2$HouseStyle = as.character(train_data_q2$HouseStyle)
train_data_q2 = train_data_q2 %>%   mutate_at(vars(HouseStyle) ,     ~ifelse(.x=="2.5Fin","1.5Unf",.x  ))
train_data_q2$HouseStyle = as.factor(train_data_q2$HouseStyle)

train_data_q2_process = preProcess(train_data_q2[,2:22], method=c("center", "scale"))
train_data_q2 =  predict(train_data_q2_process, train_data_q2)

@@

# Impute = NA in test data
test_data_q2= test_data_q2 %>% mutate_at(vars(GarageCars),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
test_data_q2= test_data_q2 %>% mutate_at(vars(BsmtFullBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
test_data_q2= test_data_q2 %>% mutate_at(vars(BsmtHalfBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))

summary(test_data_q2)
nrow(test_data_q2)
unique(train_data_q2$HouseStyle)
unique(test_data_q2$HouseStyle)

@@

`

@@

#	ANALYSIS 2
```{r message=FALSE, warning=FALSE}
one_encode_train_data_q2 =  one_hot(as.data.table(train_data_q2, dropUnusedLevels=TRUE))
one_encode_train_data_q2
one_encode_test_data_q2 =  one_hot(as.data.table(test_data_q2, dropUnusedLevels=TRUE))

@@

# lm_fit_q2 = lm(SalePrice ~.-Id
#               - SaleCondition.Family  
# -SaleType.Oth
# -MiscFeature.TenC 
# -Fence.MnWw 
# -PoolQC.Gd 
# -PavedDrive.P
# -GarageCond.Ex
# -GarageCond.None
# -GarageQual.Po
# -GarageFinish.Fin 
# -GarageType.CarPort
# -FireplaceQu.Po  
# -Functional.Sev 
# -KitchenQual.Fa
# -Electrical.None 
# -CentralAir.N 
# -HeatingQC.Po
# -Heating.Floor
# -BsmtFinType2.GLQ 
# -BsmtFinType1.LwQ  
# -BsmtExposure.None 
# -BsmtCond.Po  
# -BsmtCond.None
# -BsmtQual.Fa 
# -Foundation.Stone 
# -ExterCond.Ex  
# -ExterQual.Fa 
# -MasVnrType.BrkCmn
# -Exterior2nd.CBlock 
# -Exterior1st.CBlock
# -RoofMatl.ClyTile
# -RoofStyle.Shed  
# -HouseStyle.2.5Fin 
# -BldgType.Twnhs
# -Condition2.RRAe 
# -Condition1.RRNe 
# -Neighborhood.Blueste
# -MSZoning.RH
# -Alley.Pave 
# -Utilities.NoSeWa 
# -LotConfig.FR3 
# -LandSlope.Sev
# -Street.Grvl
# , enconded_data_train_q2)

summary(lm_fit_q2)
```

## Model Selection
### Stepwise
```{r message=FALSE, warning=FALSE}
#Stepwise Selection
stepwise_fit = ols_step_both_p(lm_fit_q2, pent =0.05, prem=0.05)
stepwise_fit
```
```{r}
stepwise_fit$predictors
```

@@

#write_csv(stepwise_submission, "../kaggleData/stepwiseSelectionPredictions.csv")

nrow(stepwise_submission)
sum(is.na(stepwise_submission))
stepwise_submission_na <- stepwise_submission %>% filter_all(any_vars(is.na(.))) 
stepwise_submission_na
```
```{r}
step_wise_vif = VIF(stepwise_model)
step_wise_vif
```

@@

```{r}
fw_model = fw_fit$model
ols_press(fw_model)
summary(fw_model)
#confint(fw_model)

@@

fw_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=fw_predictions)
fw_submission
#write_csv(fw_submission, "../kaggleData/forward SelectionPredictions.csv")

nrow(fw_submission)
sum(is.na(fw_submission))
fw_submission_na <- fw_submission %>% filter_all(any_vars(is.na(.))) 
fw_submission_na
```
```{r}
fw_vif = VIF(fw_model)
c(fw_vif)

@@

```{r}
bw_model = bw_fit$model
ols_press(bw_model)
formatC(ols_press(bw_model), format = "e", digits = 6)
summary(bw_model)
#confint(bw_model)
```

@@

bw_submission = data.frame(Id= one_encode_test_data_q2$Id, SalePrice=bw_predictions)
bw_submission
#write_csv(bw_submission, "../kaggleData/backwardsSelectionPredictions.csv")

@@

```
```{r}
bw_vif = VIF(bw_model)
c(bw_vif)

@@

```{r}
custom_train_data
train_data_q2
```

```{r}
# outliers list
outliers_forward = c(4, 54,   59,   66,   67,   70,   94,  119,  121,  138,  152,  154,  164,  179,  186,  209,  219,  239,  250,  252,  262,  305,  314,  321,  322,  331,  336,  337,  349,  350,  363,  384,  385,  401,  427,  439,  441,  474,  478,  497,  524,  528,  530,  560,  567,  569,  582,  584,
 586,  589,  592,  598,  608,  622,  633,  636,  641,  643,  656,  662,  665,  682,  686,  689,  692,  703,  713,  725,  745,  770,  775,  779,  799,  804,  811,  813,  823,  826,  841,  876,  878,  886,  898,  899,  926,  940,  962,  971, 1018, 1025, 1032, 1045, 1047, 1049, 1063, 1066,
 1069, 1128, 1143, 1156, 1169, 1170, 1174, 1176, 1182, 1183, 1217, 1268, 1269, 1285, 1299, 1311, 1323, 1325, 1327, 1329, 1360, 1387, 1389, 1397, 1416, 1424, 1441)
#outliers_forward = c(1047,770,1047,1424)

@@

selected_features_q2 = c("GrLivArea", "Neighborhood", "LotArea", "YrSold", "SaleCondition", "HouseStyle", "KitchenQual", "YearRemodAdd","GarageCars", "Fireplaces","BsmtFullBath","BsmtHalfBath","FullBath","HalfBath","BedroomAbvGr","Remodel","OverallQual", "GrLivArea2","X1stFlrSF","X2ndFlrSF","PoolArea")

@@

custom_train_data_process = preProcess(custom_train_data[,2:22], method=c("center", "scale"))
custom_train_data =  predict(custom_train_data_process, custom_train_data)

custom_test_data = data_test %>%  select(Id, selected_features_q2)
custom_test_data =  predict(custom_train_data_process, custom_test_data)

@@

```{r}
#custom_train_data

@@

```{r}
custom_model = custom_fit$model
ols_press(custom_model)
formatC(ols_press(custom_model), format = "e", digits = 6)
summary(custom_model)
#confint(custom_model)
```

@@

ols_plot_resid_fit(custom_model)
ols_plot_resid_pot(custom_model)
ols_pred_rsq(custom_model)
plot(custom_fit)
```
```{r}
custom_model_outliers$outliers$observation

@@

custom_submission = data.frame(Id= one_encode_custom_test_data$Id, SalePrice=custom_predictions)
custom_submission
#write_csv(custom_submission, "../kaggleData/customSelection3Predictions.csv")
```

@@

custom1_vif = VIF(custom_model)
c(custom1_vif)
```

```{r}
one_encode_custom_train_data_model2

```{r}
one_encode_custom_train_data_model2 = one_encode_custom_train_data

one_encode_custom_train_data_model2$index = seq.int(nrow(one_encode_custom_train_data_model2))
one_encode_custom_train_data_model2

 custom_model_1_outliers = c( 556)
#
#
#
 one_encode_custom_train_data_model2 = one_encode_custom_train_data_model2[!(one_encode_custom_train_data_model2$index %in% custom_model_1_outliers), ]
 one_encode_custom_train_data_model2
#
#
#get original data again without all the outliers. This way we can scale it using only the values we will utilize, we do this to avoid data leaking
 final_one_encode_custom_train_data_model2 = data_train[(data_train$Id %in% one_encode_custom_train_data_model2$Id), ]
 final_one_encode_custom_train_data_model2
```

```{r}
# do all the data preprossesing again
final_one_encode_custom_train_data_model2 = final_one_encode_custom_train_data_model2 %>% select(Id, selected_features_q2,  SalePrice)

# # 2.5Fin does not exist in test data so changing it to 1.5Unf
final_one_encode_custom_train_data_model2$HouseStyle = as.character(final_one_encode_custom_train_data_model2$HouseStyle)
final_one_encode_custom_train_data_model2 = final_one_encode_custom_train_data_model2 %>%   mutate_at(vars(HouseStyle) ,     ~ifelse(.x=="2.5Fin","1.5Unf",.x  ))

@@

custom2_train_data_process = preProcess(final_one_encode_custom_train_data_model2[,2:22], method=c("center", "scale"))
final_one_encode_custom_train_data_model2 =  predict(custom2_train_data_process, final_one_encode_custom_train_data_model2)

@@

#  Impute = NA in test data
final_custom_test_data= final_custom_test_data %>% mutate_at(vars(GarageCars),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
final_custom_test_data= final_custom_test_data %>% mutate_at(vars(BsmtFullBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))
final_custom_test_data= final_custom_test_data %>% mutate_at(vars(BsmtHalfBath),~ifelse(is.na(.x), median(.x, na.rm = TRUE), .x))

@@

# #References: Neighborhood_BrkSide KitchenQual_TA HouseStyle_SLvl SaleCondition_Partial
# # Manual exclusion:
# # take away PoolArea due to 0 variance warning
# #SaleCondition_AdjLand:GrLivArea2           NA         NA      NA       NA
# #SaleCondition_Alloca:GrLivArea2            NA         NA      NA       NA
# #LotArea:SaleCondition_AdjLand              NA         NA      NA       NA
# #LotArea:SaleCondition_Alloca               NA         NA      NA       NA
# #SaleCondition_Alloca:BedroomAbvGr          NA         NA      NA       NA

@@

summary(lm_fit_custom2)

ols_press(lm_fit_custom2)

@@

```{r}
custom_model2 = custom_fit2$model
ols_press(custom_model2)
formatC(ols_press(custom_model2), format = "e", digits = 6)
summary(custom_model2)
# confint(custom_model2)
```

```{r}
 ols_plot_cooksd_bar(custom_model2)
# 
custom_model_outliers2 = ols_plot_cooksd_bar(custom_model2, print_plot=F)
custom_model_outliers2
# 
ols_plot_dffits(custom_model2)
ols_plot_diagnostics(custom_model2)
# 
ols_plot_resid_fit(custom_model2)
ols_plot_resid_pot(custom_model2)
ols_pred_rsq(custom_model2)
plot(custom_fit2)
```

@@

# custom_model_outliers2$outliers$observation

@@

custom_predictions2 = c(predict(custom_model2, newdata = one_encode_custom_test_data2))
# 
# 
custom_predictions2 = data.frame(Id= one_encode_custom_test_data2$Id, SalePrice=custom_predictions2)
custom_predictions2
#write_csv(custom_predictions2, "../kaggleData/customSelection4Predictions.csv")
```
```{r}

custom2_vif = VIF(custom_model2)
c(custom2_vif)
```

```{r}
#custom_model2$terms

@@

#custom_fit3 = ols_step_both_p(lm_fit_custom2, penter=0.05, details = F)
# OverallQual        X1stFlrSF  HouseStyle_2Story  GrLivArea    KitchenQual_Gd:GrLivArea   GrLivArea2:KitchenQual_Gd

lm_fit_custom3 = lm(SalePrice ~ OverallQual  + GarageCars + 
    BsmtFullBath + KitchenQual_Ex + YearRemodAdd + Neighborhood_OldTown + 
    LotArea + GrLivArea:KitchenQual_Gd + Neighborhood_Crawfor + 
    Neighborhood_NridgHt + SaleCondition_Abnorml + Neighborhood_Somerst + 
    HalfBath + Neighborhood_Edwards + SaleCondition_Normal + 
    SaleCondition_Alloca + BsmtHalfBath + FullBath + Neighborhood_ClearCr + 
    Neighborhood_MeadowV + Neighborhood_SawyerW + Neighborhood_Mitchel + 
    Neighborhood_BrDale + SaleCondition_Family + SaleCondition_AdjLand + 
    Neighborhood_IDOTRR + YrSold + Neighborhood_NPkVill + HouseStyle_SFoyer + 
    Neighborhood_Timber + KitchenQual_Fa + Neighborhood_Sawyer + 
     Neighborhood_Blueste + Fireplaces + Neighborhood_Blmngtn + 
    Neighborhood_CollgCr + Neighborhood_Gilbert + Neighborhood_Veenker + 
    Neighborhood_StoneBr + HouseStyle_1.5Unf + Remodel + Neighborhood_SWISU + 
    HouseStyle_1.5Fin + BedroomAbvGr + HouseStyle_1Story + HouseStyle_2.5Unf + 
     Neighborhood_NWAmes + KitchenQual_Gd +  
    Neighborhood_NAmes + Neighborhood_NAmes:GrLivArea2 + Neighborhood_NoRidge + 
    Neighborhood_OldTown:GrLivArea2  + 
    Neighborhood_NridgHt:LotArea + Neighborhood_NridgHt:BedroomAbvGr + 
    Neighborhood_Somerst:GrLivArea2 + Neighborhood_StoneBr:GrLivArea2 + 
    HouseStyle_1Story:GrLivArea2 + GrLivArea:Neighborhood_Sawyer + 
    Neighborhood_Edwards:GrLivArea2 + LotArea:SaleCondition_Abnorml + 
    LotArea:HouseStyle_1Story + KitchenQual_Ex:BedroomAbvGr + 
    KitchenQual_Gd:BedroomAbvGr + Neighborhood_Somerst:LotArea + 
    Neighborhood_Edwards:LotArea + Neighborhood_Veenker:BedroomAbvGr + 
     Neighborhood_NAmes:BedroomAbvGr + 
    SaleCondition_Family:BedroomAbvGr + Neighborhood_CollgCr:BedroomAbvGr + 
    Neighborhood_StoneBr:LotArea + Neighborhood_Timber:GrLivArea2 + 
    Neighborhood_Timber:BedroomAbvGr
                , data = one_encode_custom_train_data2)
summary(lm_fit_custom3)
formatC(ols_press(lm_fit_custom3), format = "e", digits = 6)
```

```{r}
 ols_plot_cooksd_bar(lm_fit_custom3)
# 
custom_model_outliers3 = ols_plot_cooksd_bar(lm_fit_custom3, print_plot=F)
custom_model_outliers3
# 
ols_plot_dffits(lm_fit_custom3)
#ols_plot_diagnostics(lm_fit_custom3)
# 
ols_plot_resid_fit(lm_fit_custom3)
ols_plot_resid_pot(lm_fit_custom3)
ols_pred_rsq(lm_fit_custom3)
plot(lm_fit_custom3)
```

custom_predictions3 = c(predict(lm_fit_custom3, newdata = one_encode_custom_test_data2))
# 
# 
custom_predictions3 = data.frame(Id= one_encode_custom_test_data2$Id, SalePrice=custom_predictions3)
custom_predictions3
write_csv(custom_predictions3, "../kaggleData/customSelection5Predictions.csv")
```
```{r}

custom3_vif = VIF(lm_fit_custom3)
c(custom3_vif)
```
